Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-08-13 Manuscript/Manuscript.Rmd
updated final data
RT outliers updated -- now calculates only RTs in face trials

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-07_15-04-27.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

>>>>

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-13_12-52-10.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### 2019-08-13 Manuscript/Manuscript.tex
updated final data
RT outliers updated -- now calculates only RTs in face trials

\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.

>>>>

\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}

Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
